Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-23 paper/manuscript.tex
added fracsurvive supp table

\usepackage{newfloat}
\DeclareFloatingEnvironment[name={Figure}]{suppfigure}
\renewcommand{\thesuppfigure}{S\arabic{suppfigure}}

@@

\subsection*{Mutant virus selections with antibody and deep sequencing}
Library selections and deep sequencing were performed as previously described in~\cite{doud2017complete}. 
We conducted the antibody selections using the mutant virus libraries from~\cite{doud2016accurate}. 
We diluted the virus libraries to a concentration of $1 \times 10^{6}$ TCID$_{50}$ per ml and incubated the virus dilutions with an equal volume of antibody at the intended concentration.
We then incubated the virus-antibody mixture at 37$^\circ$C for 1.5 hours
Each selection was done in biological triplicate at the antibody concentrations shown in Figure~\ref{fig:neutcurves} concentrations, and technical replicates of some of the concentrations were also performed. 
To estimate the fraction of the overall library surviving selection, denoted as $\gamma$ in this paper, we made duplicate 10-fold serial dilutions of each of the virus libraries to use as a standard curve of infectivity. 
qRT-PCR of the standard curves were performed as previously described in~\cite{doud2017complete} using qPCR primers for WSN influenza nucleoprotein (NP) to quantify viral infectivity and primers for canine GAPDH to correct for RNA amounts.
Next, we fit a linear regression of the log(infectious dose) versus the mean difference in qPCR Ct values between NP and GAPDH to estimate the total library fraction infectivity after antibody selection.

@@

>>>>

\usepackage{newfloat}
\DeclareFloatingEnvironment[name={Figure}]{suppfigure}
\renewcommand{\thesuppfigure}{S\arabic{suppfigure}}
\DeclareFloatingEnvironment[name={Table}]{supptable}
\renewcommand{\thesupptable}{S\arabic{supptable}}

@@

\subsection*{Mutant virus libraries}
The mutant virus libraries are those described in \citet{doud2016accurate}, and were produced in full biological triplicate.
Briefly, these libraries were generated by using codon mutagenesis~\citep{bloom2014experimentally} to introduce random codon mutations into plasmid-encoded HA, and then generating the virus libraries using a helper-virus strategy that avoids the bottlenecks associated with standard influenza reverse genetics.
Full details of the library generation and sequencing statistics that quantify how completely each of the triplicate libraries covers the possible amino-acid mutations are in \citet{doud2016accurate}.

\subsection*{Mutational antigenic profiling}
The mutational antigenic profiling was performed as described in \citet{doud2017complete}. 
Briefly, we diluted each virus libraries to a concentration of $10^{6}$ TCID$_{50}$ per ml and incubated the virus dilutions with an equal volume of antibody at the intended concentration at 37$^\circ$C for 1.5 hours.
The final antibody concentrations in these mixtures are shown in Figure~\ref{fig:neutcurves} concentrations.
We performed three fully independent replicates of each selection using the three replicate mutant virus libraries.
In addition, we performed technical replicates (independent neutralization experiments on the \emph{same} virus library) in some cases as indicated in Figure~\ref{suppfig:corr}.
The virus-antibody mixtures were used to infect cells, and viral RNA was extracted, reverse-transcribed, and PCR amplified as described in \citet{doud2017complete}.
In order to obtain high accuracy in the Illumina deep sequencing, we used the barcoded-subamplicon sequencing strategy described in \citet{doud2017complete}, which is a slight modification of the strategy of \citet{wu2014high}.

We also estimated the overall fraction of virions surviving each antibody selection.
These fractions are denoted by $\gamma$ in this paper.
The average of these fractions across libraries are reported in Figure~\ref{fig:neutcurves}, and the values for each individual replicate are in Table~\ref{supptab:fracsurvive}.
\comment{I AM HERE}
we made duplicate 10-fold serial dilutions of each of the virus libraries to use as a standard curve of infectivity. 
qRT-PCR of the standard curves were performed as previously described in~\cite{doud2017complete} using qPCR primers for WSN influenza nucleoprotein (NP) to quantify viral infectivity and primers for canine GAPDH to correct for RNA amounts.
Next, we fit a linear regression of the log(infectious dose) versus the mean difference in qPCR Ct values between NP and GAPDH to estimate the total library fraction infectivity after antibody selection.

@@

\begin{supptable}
\centering
\begin{tabular}{cccc}
antibody &  concentration ($\mu$g/ml) &  replicate &  fraction surviving \\
\hline
FI6v3 &            0.1 &  1a &             0.01662 \\
 FI6v3 &            0.1 &  1b &             0.01390 \\
FI6v3 &            0.2 &  1a &             0.00465 \\
FI6v3 &            0.2 &  1b &             0.00345 \\
FI6v3 &            0.1 &  2 &             0.02322 \\
FI6v3 &            0.2 &  2 &             0.00278 \\
FI6v3 &            0.1 &  3 &             0.00903 \\
FI6v3 &            0.2 &  3 &             0.00144 \\
S139/1 &          100.0 &  1 &             0.02490 \\
S139/1 &          200.0 &  1 &             0.01470 \\
S139/1 &          300.0 &  1 &             0.01270 \\
S139/1 &          100.0 &  2 &             0.02190 \\
S139/1 &          200.0 &  2 &             0.01720 \\
S139/1 &          300.0 &  2 &             0.00854 \\
S139/1 &          100.0 &  3 &             0.05180 \\
S139/1 &          200.0 &  3 &             0.04060 \\
S139/1 &          300.0 &  3 &             0.03750 \\
C179 &            1.0 &    1a &             0.00941 \\
C179 &            1.0 &    1b &             0.00890 \\
C179 &            1.0 &    1c &             0.00960 \\
C179 &            2.5 &    1 &             0.00450 \\
C179 &            1.0 &    2 &             0.00554 \\
C179 &            2.5 &    2 &             0.00198 \\
C179 &            1.0 &    3 &             0.00256 \\
C179 &            2.5 &    3 &             0.00100 \\
\end{tabular}
\caption{\label{supptab:fracsurvive}
The total fraction of virions surviving each antibody treatment at each concentration as estimated by qPCR.
These are the quantities referred to as $\gamma$.
This table shows the values for the broad antibodies; values for the narrow H17-L17, H17-L10, and H17-L7 antibodies are reported in \citet{doud2017complete}.
}
\end{supptable}
